---
title: "seaportai"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{css}
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
```




```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(knitr)
library(reticulate)
library(data.table)
library(rsconnect)
py_install("pandas")
py_install("lifetimes")
```




**CLV**
===========================================

```{r, e}
fileInput("file","Upload",accept = c(".csv"))
options(shiny.maxRequestSize=100*1024^2)
actionButton("submit", "Submit")
v <- reactiveValues()
renderUI(v[["py_chunk"]])

observeEvent(
  input$submit,
  {
    var <- input$text
    data=read.csv(input$file$datapath)
    # Each chunk line is an element of the vector
    py_code <- c(
      "```{python,echo=FALSE}",

"import pandas as pd",
"import numpy as np",
"import seaborn as sns",
"import datetime as dt",
"import lifetimes",
"from lifetimes import plotting",
"from lifetimes import utils",
"from lifetimes import estimation",
"from lifetimes.utils import summary_data_from_transaction_data",
"from lifetimes import BetaGeoFitter",
"from lifetimes.plotting import plot_period_transactions",
"from lifetimes.utils import calibration_and_holdout_data",
"from lifetimes import GammaGammaFitter",
"import tkinter",
"from tkinter import *",
"import seaborn as sns",

"data=pd.DataFrame(r.data)",


"data['price']=data.Quantity*data.UnitPrice",

"data['InvoiceDate'] = pd.to_datetime(data['InvoiceDate']).dt.date",

"data = data[pd.notnull(data['CustomerID'])]",

"data = data[(data['Quantity']>0)]",

"cols_of_interest = ['CustomerID', 'InvoiceDate', 'price']",

"data = data[cols_of_interest]",

"data1 = summary_data_from_transaction_data(data, 'CustomerID', 'InvoiceDate', monetary_value_col='price', observation_period_end='2011-9-12')",
"bgf = BetaGeoFitter(penalizer_coef=0.0)",

"bgf.fit(data1['frequency'], data1['recency'], data1['T'])",
"t = 1" ,

"data1['predicted_purchases'] = bgf.conditional_expected_number_of_purchases_up_to_time(t, data1['frequency'],    data1['recency'], data1['T'])",


 "summary_cal_holdout = calibration_and_holdout_data(data, 'CustomerID', 'InvoiceDate',
                                         calibration_period_end='2011-08-06',
                                         observation_period_end='2011-9-12' ) " , 
                                        
"returning_customers_summary = data1[data1['frequency']>0]",

"ggf = GammaGammaFitter(penalizer_coef = 0)",

"ggf.fit(returning_customers_summary['frequency'],
        returning_customers_summary['monetary_value'])",
        
"bgf.fit(data1['frequency'], data1['recency'], data1['T'])",

"out=ggf.customer_lifetime_value(
  bgf, #the model to use to predict the number of future transactions
  data1['frequency'],
  data1['recency'],
  data1['T'],
  data1['monetary_value'],
  time=90, # months
  discount_rate=0.01)",
"output=np.round(pd.DataFrame(out),decimals=2)",
"output=output.iloc[1:]",
"output.reset_index(level=0, inplace=True)",

"a=output[output['clv']<=2500]",
"b=output[(output['clv'] >2500) & (output['clv'] <= 7500)]",
"c=output[output['clv'] > 7500]",
"a.columns = ['CustomerID','less profitable customers']",
"b.columns = ['CustomerID','medium profitable customers']",
"c.columns = ['CustomerID','more profitable customers']",

# "ss=pd.DataFrame({'less profitable customers':a,
#                              'medium profitable customers':b,
#                              'more profitable customers':c})",

"print(c)",
      "```"
    )
  "```"
  "**sdkjfh**"
"=============================="
"sns.barplot(x='CustomerID', y='clv', data=a, saturation=0.8)"
    
    # Make sure knitr's converting to HTML
    knitr::render_html()
    # Then store the output in the reactive value
    v[["py_chunk"]] <- HTML(knitr::knit(text = py_code))
  }
)
```

**GRAPH**
===================================

```{r, echo=FALSE}
library("knitr")


aa=py$a
bb=py$b
cc=py$c

# a=data[data$clv <= 2500,]
# #names(a)[names(a) == "clv"] = "less profitable customers"
# b=data[data$clv > 2500 & data$clv <=7500,]
# #names(b)[names(b) == "clv"] = "medium profitable customers"
# c=data[data$clv > 7500,]
# names(c)[names(c) == "clv"] = "more profitable customers"
zz= merge(aa,bb ,all = TRUE)
xx= merge(zz,cc,all = TRUE)

xx[is.na(xx)] <- 0
xx

```


